A family of accessibility measures derived from spatial interaction principles

### 2025-05-20 paper/manuscript.qmd
fixed a typo

As Wilson explicitly noted, origin and destination weights defined in the spatial interaction model *can* be defined using any unit. Accessibility, however, is often presented and understood as a zonal summary of *potential* for interaction between origins and destinations that contain inherently different units. Arriving at the doubly constrained case through the unconstrained, totally, and singly constrained cases make the connection between the *potential* for spatial interaction (accessibility) and *realized* potential for spatial interaction more interpretable. Namely, by demonstrating that these members of the accessibility family all derive from the same root and can be derived from Wilson's original formulation, this more clearly demonstrates what *potential* is, within the context of spatial interaction modelling.

>>>>

As Wilson explicitly noted, origin and destination weights defined in the spatial interaction model *can* be defined using any unit. Accessibility, however, is often presented and understood as a zonal summary of *potential* for interaction between origins and destinations that contain inherently different units. Arriving at the doubly constrained case through the unconstrained, total, and singly constrained cases make the connection between the *potential* for spatial interaction (accessibility) and *realized* potential for spatial interaction more interpretable. Namely, by demonstrating that these members of the accessibility family all derive from the same root and can be derived from Wilson's original formulation, this more clearly demonstrates what *potential* is, within the context of spatial interaction modelling.

### 2025-05-20 paper/manuscript.tex
fixed a typo

As Wilson explicitly noted, origin and destination weights defined in
the spatial interaction model \emph{can} be defined using any unit.
Accessibility, however, is often presented and understood as a zonal
summary of \emph{potential} for interaction between origins and
destinations that contain inherently different units. Arriving at the
doubly constrained case through the unconstrained, totally, and singly
constrained cases make the connection between the \emph{potential} for
spatial interaction (accessibility) and \emph{realized} potential for
spatial interaction more interpretable. Namely, by demonstrating that
these members of the accessibility family all derive from the same root
and can be derived from Wilson's original formulation, this more clearly
demonstrates what \emph{potential} is, within the context of spatial
interaction modelling.

@@

\section{References}\label{references}

>>>>

As Wilson explicitly noted, origin and destination weights defined in
the spatial interaction model \emph{can} be defined using any unit.
Accessibility, however, is often presented and understood as a zonal
summary of \emph{potential} for interaction between origins and
destinations that contain inherently different units. Arriving at the
doubly constrained case through the unconstrained, total, and singly
constrained cases make the connection between the \emph{potential} for
spatial interaction (accessibility) and \emph{realized} potential for
spatial interaction more interpretable. Namely, by demonstrating that
these members of the accessibility family all derive from the same root
and can be derived from Wilson's original formulation, this more clearly
demonstrates what \emph{potential} is, within the context of spatial
interaction modelling.

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}
